---
title: "P8105_Homework01"
author: "Lin_Feng_lf2649"
date: "September 19, 2020"
output: github_document
---


### Problem 0.1

The link is https://github.com/Lin322/p8105_hw1_LF2649. 


### Problem 0.2

This “problem” focuses on correct styling for your solutions to Problems 1 and 2. We will look for:

 * meaningful variable / object names
 * readable code (one command per line; adequate whitespace and indentation; etc)
 * clearly-written text to explain code and results
 * a lack of superfluous code (no unused variables are defined; no extra library calls; ect



# Problem 1

Create a data frame comprised of:

* random sample of size 10 from a standard Normal distribution
* logical vector indicating whether elements of the sample are greater than 0
* character vector of length 10
* factor vector of length 10, with 3 different factor “levels”


```{r problem_1 }
library(tidyverse)

p1_df = tibble(
 vec_numrc = rnorm(10, mean = 0, sd = 1),
 vec_numrc_pos = vec_numrc > 0,
 vec_char = c("The", "character","vector","has","to","be","exactly","ten","words","here"),
 vec_factor = factor(c("A","A","B","B","C","C","C","C","C","C"))
)

p1_df



```


Try to take the mean of each variable in your dataframe. What works and what doesn’t?

 * R can caculate mean for mumeric and logical data, but cannot for character and foctor data. 

```{r means}
vec_numrc = rnorm(10, mean = 0, sd = 1)

mean(vec_numrc)


vec_numrc_pos = vec_numrc > 0

mean(vec_numrc_pos)


vec_char = c("The", "character","vector","has","to","be","exactly","ten","words","here")

mean(vec_char)


vec_factor = factor(c("A","A","B","B","C","C","C","C","C","C"))

mean(vec_factor)



```



